Figures

### 2020-07-08 figures/01_contrasts.Rmd
finish out bathy comparison fig, closes #12

```{r gg_effort, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 3.5}
# compare characteristics of bathy lakes versus overall lakes

@@

lg$urban_distance <- apply(
  st_distance(
    st_transform(
      LAGOSUS::coordinatize(lg, crs = 4326), 
      LAGOSUSgis:::albers_conic()),
    urbanareas), 
  1, function(x) x[which.min(x)])

cowplot::plot_grid(
  gg_quantdot(lg, lagos_effort, "lake_maxdepth_m"), 
  gg_quantdot(lg, lagos_effort, "lake_waterarea_ha") +
    scale_y_log10(), 
  gg_quantdot(lg, lagos_effort, "urban_distance"),
  ncol = 1)
```

>>>>

```{r gg_effort, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 3.7, fig.width=2.7}
# compare characteristics of bathy lakes versus overall lakes

@@

lg$urban_distance <- apply(
  st_distance(
    st_transform(
      LAGOSUS::coordinatize(lg, crs = 4326), 
      LAGOSUSgis:::albers_conic()),
    urbanareas), 
  1, function(x) x[which.min(x)])
lg$urban_distance <- lg$urban_distance * 0.001 # m to km

theme_opts <- theme(axis.title.x = element_blank())
cowplot::plot_grid(
  gg_quantdot(lg, lagos_effort, "lake_maxdepth_m") +
    ylab("Max depth (m) \n") +
    theme_opts +
    theme(axis.text.x = element_blank()), 
  gg_quantdot(lg, lagos_effort, "lake_waterarea_ha") +
    scale_y_log10() +
    ylab("Area (ha)") +
    theme_opts +
    theme(axis.text.x = element_blank()), 
  gg_quantdot(lg, lagos_effort, "urban_distance") +
    scale_y_log10() +
    ylab("Distance to urban (km)") +
    theme_opts,
  rel_heights = c(0.85, 0.85, 1),  ncol = 1)
```

### 2020-07-08 manuscript/appendix.Rmd
finish out bathy comparison fig, closes #12

>>>>

```{r gg_effort, fig.cap = "Comparison between characteristics of lakes with bathymetry data against lakes with depth from other sources. Distance to urban areas uses data from the 2018 US Census Urban and Rural Classification.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/gg_effort-1.pdf")
```
